---
title: "Soft Clip Report"
output:
  html_document:
    theme: readable
    toc: TRUE
    toc_depth: 3
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
    number_sections: TRUE
date: "`r format(Sys.time(), '%d %B, %Y')`"
params: 
  run:  
  s3_dir:
  omit:
  report_threshold: 
  output_dir: 'default'
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DT)

```

```{r,include = FALSE}
base = "https:/XXX"
aws_base = "https:/XXX"
output = paste0(aws_base,params$s3_dir, "/")
multiqc = paste0(base,params$s3_dir,"/summary/", params$job,"_multiqc_report.html")
report = paste0(base,params$s3_dir,"/summary/sv_report.html")

```
```{r load-packages, include=FALSE}
library(knitr)
library(DT)
Sys.setenv("RSTUDIO_PANDOC"="XXXX")
```
SoftClip results for **`r params$run`**. 

Output: reports, tables, logs, and more available on S3 <a href=`r output` target="_blank">here</a>.

# Experiment Parameters

**Samples:**
```{r, echo=FALSE}
samples <- read.csv(file = 'samples.csv')
knitr::kable(samples,row.names = FALSE,  col.names = gsub("[.]", " ", names(samples)))

      
```

## Table of soft clipped counts
*Count for each position that has been soft clipped. Soft clipped count peak is called by scipy.signal after smmoothing the curve using savgol_filter. The peak threshold is prominence = avg/2. A threshold of **`r params$report_threshold`**% is used.*
```{r,echo=FALSE}
soft_clipped_df <- read.csv(file = 'results/soft_clipped_peak_df.csv')[ ,3:9]
if(nrow(soft_clipped_df)>0){
  datatable(soft_clipped_df)
# knitr::kable(soft_clipped_df,row.names = FALSE, col.names = gsub("[.]", " ", names(soft_clipped_df)))
}else{
    cat("No significant soft clipped position peaks found. \n")
  }

```
# Soft Clip Graphs
*Regions that are heavily soft clipped are indicative of structural variants.
```{r,echo=FALSE,results= "asis"}
for(lib in samples$Libraries){
  label = samples[which(samples$Libraries == lib),]
  cat("  \n##",  lib," ",label[,3], "  \n")
  image_name = paste0('results/',lib, '_soft_clipped_pct.png')
  cat("  \n", "![", image_name, "](", image_name, ")", "  \n",sep="")
}
```